Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-21 JASA-template.tex
Small updates, clarify n.

Let an observational study give us the outcomes $Y=(Y_1, \dots, Y_n)$ along with 
corresponding treatment indicators $T=(T_1, \dots, T_n)$. Then the
treatment 
effect in the population is given by the expectation of the difference
in outcomes between the treatment and controls:
\begin{align}
	\delta = \mathbb{E}(Y\mid T =1) - \mathbb{E}(Y\mid T=0).
\end{align}
Similarly, the individual causal
effect of treatment $T_i$ on outcome $Y_i$ is given by:
\begin{align}
	\delta_i \coloneqq \mathbb{E}(Y_i\mid T_i=1) - \mathbb{E}(Y_i\mid T_i=0).
\end{align}
That is, we are interested in the difference between the outcomes when the $i$-th subject receives
the treatment and when 
%$i$-th subject 
it remains as a control.

>>>>

Let an observational study on $n$ individuals give us the outcomes $Y\coloneqq(Y_1, \dots, Y_n)$ along with 
corresponding treatment indicators $T\coloneqq(T_1, \dots, T_n)$. Then the
treatment 
effect in the population is given by the expectation of the difference
in outcomes between the treatment and controls:
%%% MT to TB: I don't understand this equation; since Y and T are vectors, is \delta simply \delta_1,\dots,\delta_n? I think something else is meant? or remove this equation?
\begin{align}
	\delta = \mathbb{E}(Y\mid T =1) - \mathbb{E}(Y\mid T=0).
\end{align}
Similarly, the individual causal
effect of treatment $T_i$ on outcome $Y_i$ is given by:
\begin{align}
	\delta_i \coloneqq \mathbb{E}(Y_i\mid T_i=1) - \mathbb{E}(Y_i\mid T_i=0).
\end{align}
That is, we are interested in the difference between the outcomes when the $i$-th subject receives
the treatment and when 
%$i$-th subject 
it remains as a control.
